SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-27 scipy-1.0/paper.tex

% PhD Mayo Clinic, started faculty position at BYU in 2001
By the late 1990s, discussions appeared on Matrix-SIG,
expressing a desire for a complete scientific data analysis environment\cite{Travis-Keynote-2010}.
Travis Oliphant, a PhD student at the Mayo Clinic,
released a number of packages\cite{Travis-some-modules,Travis-enhance} 
that built on top of the Numeric array
package, and provided algorithms for signal processing, special
functions, sparse matrices, quadrature, optimization, Fast Fourier
Transforms, and more.  One of these packages, Multipack, was a set of
extension modules that wrapped Fortran and C libraries such as
ODEPACK, QUADPACK, and MINPACK, to solve and minimize nonlinear
equations, integrate differential equations, and fit splines (the
latter implemented by Pearu Peterson).  Robert Kern, then an
undergraduate student (and currently a SciPy core developer), provided
compilation instructions under Windows.
% 2001 PhD Tallinn Technical University
Around the same time, Pearu Peterson, a PhD student from Estonia,
released f2py\cite{Pearu-f2py-mail}, a command line tool for binding Python and Fortran
codes, and wrote modules for linear algebra and interpolation.
% Graduated 1999, Duke
Eric Jones, while a graduate student at Duke, wrote a number of
packages to support his dissertation, including a parallel job
scheduler and genetic optimizer.
% Graduated 1998, PhD from Brown, 97–99 postdoc at Harvard Medical
% School; at Harvard ever since
%
% https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
Gary Strangman, a postdoctoral fellow at Harvard Medical School,
published several descriptive and inferential statistical 
routines\cite{Strangman-modules}.

>>>>

% PhD Mayo Clinic, started faculty position at BYU in 2001
By the late 1990s, discussions appeared on Matrix-SIG
expressing a desire for a complete scientific data analysis environment\cite{Travis-Keynote-2010}.
Travis Oliphant, a PhD student at the Mayo Clinic,
released a number of packages\cite{Travis-some-modules,Travis-enhance} 
that built on top of the Numeric array
package, and provided algorithms for signal processing, special
functions, sparse matrices, quadrature, optimization, Fast Fourier
Transforms, and more.  One of these packages, Multipack, was a set of
extension modules that wrapped Fortran and C libraries such as
ODEPACK, QUADPACK, and MINPACK, to solve and minimize nonlinear
equations, integrate differential equations, and fit splines (the
latter implemented by Pearu Peterson).  Robert Kern, then an
undergraduate student (and currently a SciPy core developer), provided
compilation instructions under Windows.
% 2001 PhD Tallinn Technical University
Around the same time, Pearu Peterson, a PhD student from Estonia,
released F2PY\cite{peterson2009f2py}, a command line tool for binding Python and Fortran
codes, and wrote modules for linear algebra and interpolation.
% Graduated 1999, Duke
Eric Jones, while a graduate student at Duke, wrote a number of
packages to support his dissertation, including a parallel job
scheduler and genetic optimizer.
% Graduated 1998, PhD from Brown, 97–99 postdoc at Harvard Medical
% School; at Harvard ever since
%
% https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%
Gary Strangman, a postdoctoral fellow at Harvard Medical School,
published several descriptive and inferential statistical 
routines\cite{Strangman-modules}.
